---
title: catsr_readme
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# catsr

<!-- badges: start -->
[![R-CMD-check](https://github.com/FlukeAndFeather/catsr/workflows/R-CMD-check/badge.svg)](https://github.com/FlukeAndFeather/catsr/actions)
[![codecov](https://codecov.io/gh/FlukeAndFeather/catsr/branch/master/graph/badge.svg?token=006B4PEFI0)](https://codecov.io/gh/FlukeAndFeather/catsr)
<!-- badges: end -->

catsr reads and visualizes CATS PRH files.

## Installation

You can install catsr from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("FlukeAndFeather/catsr")
```

## Reading data

Read a CATS PRH file in NetCDF format. The .nc file for deployment mn200312-58 is included in the package.

```{r read}
library(catsr)
nc_path <- system.file("extdata", "mn200312-58_prh10.nc", package = "catsr")
mn200312_58_from_nc <- read_nc(nc_path)
```

## Visualizing data

Examine PRH variables (e.g. depth, pitch, and roll) in an interactive plot. This package also provides deployment mn200312-58 directly for use in R (`mn200312_58`). GitHub READMEs don't support interaction, so we show a screenshot here instead.

```{r plot}
view_cats(mn200312_58, c("p", "pitch", "roll"))
```

Triaxial variables (such as accelerometry - `aw`) are represented in multiple colors.

```{r plot_triax}
view_cats(mn200312_58, c("p", "aw", "mw"))
```

Explore the animal's 3d movement trajectory.

```{r plot_3d}
view_cats_3d(mn200312_58)
```
